---
title: "Regression Analysis for Demog-Staging-ADI Data -- Comparison of Race/Ethnicity and ADI"
author: "Steph Reynolds (Stephanie.Reynolds@ucsf.edu)"
date: "`r format(Sys.time(), '%b %d, %Y  %H:%M %p')`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Background

## Project

MINDSCAPE: Modeling of infectious network dynamics for surveillance, control and prevention enhancement

## Description

This file reads in the demographics, Covid staging, and ADI data (`dm_stg_adi_7.19.21.rds`) and fits a logistic regression model with readmit (`readmit`) as the outcome. Primary and secondary outcomes for full regression analysis can be found below.

## Primary Outcome

-   Morbidity and Mortality (`severe_stg`) -\> All patients who reached a max stage of 6+ (severe) were recoded as severe_stg = 1

## Secondary Outcomes

-   Length of Stay (`LOS`) -\> Length of stay that patients were hospitalized
    -   Only patients who were hospitalized for \>= 1 day - aka inpatients - were included in the regression analysis.
-   Readmit (`readmit`) --\> Patients who were readmitted to hospital within 30(?) days

# Load required packages

```{r Load required packages, include=F}
library(tidyverse)
library(tidymodels)
library(performance) # to calculate model performance and check model assumptions
library(sjPlot) # to create tables from regression models 
```

# Import and preview data

```{r Read in df}
df <- readRDS("/Users/sreynolds2/Documents/GitHub/MS-ADI/data/dm_stg_adi_7.19.21.rds")

head(df, n=10)
```

# Primary Outcome: Severe morbidity and mortality (`severe_stg`)

## SMM null model 

```{r Null model of SMM}
# Null model of SMM 
m_SMM_null <- glm(severe_stg ~ 1, data = df, family = 'binomial')

# Summarize regression output 
summary(m_SMM_null)
```

## SMM model with `pat_race`, `ethnicity`, and `ADI`

```{r Full model of SMM}
# Full model of SMM -- includes race, ethnicity, and ADI 
m_SMM_full <- glm(severe_stg ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + ADI + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_SMM_full), confint.default(m_SMM_full, level=0.95)))

# Summarize regression output 
summary(m_SMM_full)

# Check model assumptions
check_model(m_SMM_full)

# Check model performance 
model_performance(m_SMM_full)
```

## SMM model without `pat_race` and `ethnicity`

```{r SMM model without race/ethnicity}
# Model without race/ethnicity 
m_SMM_no_race <- glm(severe_stg ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + ADI + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_SMM_no_race), confint.default(m_SMM_no_race, level=0.95)))

# Summarize regression output 
summary(m_SMM_no_race)

# Check model assumptions
check_model(m_SMM_no_race)

# Check model performance 
model_performance(m_SMM_no_race)
```

## SMM model without `ADI`

```{r SMM model without ADI}
# Model without ADI  
m_SMM_no_ADI <- glm(severe_stg ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_SMM_no_ADI), confint.default(m_SMM_no_ADI, level=0.95)))

# Summarize regression output 
summary(m_SMM_no_ADI)

# Check model assumptions
check_model(m_SMM_no_ADI)

# Check model performance 
model_performance(m_SMM_no_ADI)
```

## SMM model without `pat_race`, `ethnicity`, or `ADI`

```{r SMM model, without ADI or race/ethnicity}
# Model without ADI or race/ethnicity 
m_SMM_noADIorRace <- glm(severe_stg ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_SMM_noADIorRace), confint.default(m_SMM_noADIorRace, level=0.95)))

# Summarize regression output 
summary(m_SMM_noADIorRace)

# Check model assumptions
check_model(m_SMM_noADIorRace)

# Check model performance 
model_performance(m_SMM_noADIorRace)
```

## Create table to compare results from SMM regression models

```{r Create table to compare SMM models}
tab_model(m_SMM_full, m_SMM_noADIorRace, m_SMM_no_ADI, m_SMM_no_race,
                  show.reflvl = T,
                  p.style = "numeric_stars",
          dv.labels = c("Full Model", "Model without ADI or Race/Ethnicity", "Model without ADI", "Model without Race/Ethnicity"))

#pred.labels = c("Intercept", "Age", "Sex: Male", "Non-Smoker", "Smoking: Unknown", "Charlson Comorbidity Index", "Marital Status: Paired", "Marital Status: Unk/Dec", "Language: Not English", "Insurance Type: Private", "Race: Asian", "Race: Black", "Race: White", "Ethnicity: Hispanic", "Ethnicity: Not Hispanic", "Area Deprivation Index", "Admission Stage"),
```

# Compare SMM model performance 

```{r Compare SMM model performance}

# Test performance - compares BF, Omega2, p(Omega2), LR, p(LR)
performance::test_performance(m_SMM_full, m_SMM_noADIorRace, m_SMM_no_ADI, m_SMM_no_race)

# Compare performance - compares AIC, BIC, Tjur's R2, RMSE, Sigma, Log Loss, PCP
result <- compare_performance(m_SMM_full, m_SMM_noADIorRace, m_SMM_no_ADI, m_SMM_no_race)

# Spiderweb plot of result - different indices are normalized and larger values indicate better model performance. Hence, points closer to the center indicate worse fit indices.
plot(result)

# Test Bayes Factor - compares BIC 
performance::test_bf(m_SMM_full, m_SMM_noADIorRace, m_SMM_no_ADI, m_SMM_no_race)

# Same as above
result_bf <- bayestestR::bayesfactor_models(m_SMM_full, m_SMM_noADIorRace, m_SMM_no_ADI, m_SMM_no_race, denominator = 1)
as.matrix(result_bf)

# Vuong Test - compares Omega2, p(Omega2), LR, and p(LR)
# Can't use this to compare all 4 models at once, since they are not nested at that point.
test_vuong(m_SMM_full, m_SMM_no_race)
```


# Secondary Outcome: Length of Stay (`hospital_LOS`)

## LOS model with `pat_race`, `ethnicity`, and `ADI`

```{r Full model of LOS}
# Full model of LOS -- includes race, ethnicity, and ADI 
m_LOS_full <- lm(hospital_LOS ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + ADI + admission_stage + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_LOS_full), confint.default(m_LOS_full, level=0.95)))

# Summarize regression output 
summary(m_LOS_full)

# Check model assumptions
check_model(m_LOS_full)

# Check model performance 
model_performance(m_LOS_full)
```

## LOS model without `pat_race` and `ethnicity`

```{r LOS model without race/ethnicity}
# Model without race/ethnicity 
m_LOS_no_race <- lm(hospital_LOS ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + ADI + admission_stage + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_LOS_no_race), confint.default(m_LOS_no_race, level=0.95)))

# Summarize regression output 
summary(m_LOS_no_race)

# Check model assumptions
check_model(m_LOS_no_race)

# Check model performance 
model_performance(m_LOS_no_race)
```

## LOS model without `ADI`

```{r LOS model without ADI}
# Model without ADI  
m_LOS_no_ADI <- lm(hospital_LOS ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + admission_stage + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_LOS_no_ADI), confint.default(m_LOS_no_ADI, level=0.95)))

# Summarize regression output 
summary(m_LOS_no_ADI)

# Check model assumptions
check_model(m_LOS_no_ADI)

# Check model performance 
model_performance(m_LOS_no_ADI)
```

## LOS model without `pat_race`, `ethnicity`, or `ADI`

```{r LOS model, without ADI or race/ethnicity}
# Model without ADI or race/ethnicity 
m_LOS_noADIorRace <- lm(hospital_LOS ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + admission_stage + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_LOS_noADIorRace), confint.default(m_LOS_noADIorRace, level=0.95)))

# Summarize regression output 
summary(m_LOS_noADIorRace)

# Check model assumptions
check_model(m_LOS_noADIorRace)

# Check model performance 
model_performance(m_LOS_noADIorRace)
```

## Create table to compare results from LOS regression models

```{r Create table to compare LOS models}
tab_model(m_LOS_full, m_LOS_noADIorRace, m_LOS_no_ADI, m_LOS_no_race,
                  show.reflvl = T,
                  p.style = "numeric_stars",
          dv.labels = c("Full Model", "Model without ADI or Race/Ethnicity", "Model without ADI", "Model without Race/Ethnicity"))
```

# Secondary Outcome: Readmit (`readmit`)

## Readmit model with `pat_race`, `ethnicity`, and `ADI`

```{r Full model of Readmit}
# Full model of readmit -- includes race, ethnicity, and ADI 
m_readmit_full <- glm(readmit ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + ADI + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_readmit_full), confint.default(m_readmit_full, level=0.95)))

# Summarize regression output 
summary(m_readmit_full)

# Check model assumptions
check_model(m_readmit_full)

# Check model performance 
model_performance(m_readmit_full)
```

## Readmit model without `pat_race` and `ethnicity`

```{r Readmit model without race/ethnicity}
# Model without race/ethnicity 
m_readmit_no_race <- glm(readmit ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + ADI + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_readmit_no_race), confint.default(m_readmit_no_race, level=0.95)))

# Summarize regression output 
summary(m_readmit_no_race)

# Check model assumptions
check_model(m_readmit_no_race)

# Check model performance 
model_performance(m_readmit_no_race)
```

## Readmit model without `ADI`

```{r Readmit model without ADI}
# Model without ADI  
m_readmit_no_ADI <- glm(readmit ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_readmit_no_ADI), confint.default(m_readmit_no_ADI, level=0.95)))

# Summarize regression output 
summary(m_readmit_no_ADI)

# Check model assumptions
check_model(m_readmit_no_ADI)

# Check model performance 
model_performance(m_readmit_no_ADI)
```

## Readmit model without `pat_race`, `ethnicity`, or `ADI`

```{r Readmit model, without ADI or race/ethnicity}
# Model without ADI or race/ethnicity 
m_readmit_noADIorRace <- glm(readmit ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + admission_stage + BMI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_readmit_noADIorRace), confint.default(m_readmit_noADIorRace, level=0.95)))

# Summarize regression output 
summary(m_readmit_noADIorRace)

# Check model assumptions
check_model(m_readmit_noADIorRace)

# Check model performance 
model_performance(m_readmit_noADIorRace)
```

# Create table to compare results from readmit regression models

```{r Create table to compare readmit models}
tab_model(m_readmit_full, m_readmit_noADIorRace, m_readmit_no_ADI, m_readmit_no_race,
                  show.reflvl = T,
                  p.style = "numeric_stars",
          dv.labels = c("Full Model", "Model without ADI or Race/Ethnicity", "Model without ADI", "Model without Race/Ethnicity"))
```

