---
title: "Regression Analysis for Demog-Staging-ADI Data -- Charlson Comorbidity Index & Severity at Admission"
author: "Steph Reynolds (Stephanie.Reynolds@ucsf.edu)"
date: "`r format(Sys.time(), '%b %d, %Y  %H:%M %p')`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Background

## Project

MINDSCAPE: Modeling of infectious network dynamics for surveillance, control and prevention enhancement

## Description

This file reads in the demographics and COVID staging data (`dm_stg_adi_7.19.21.rds`) and fits 2 linear regression models with the following as the response variables:

1.  Charlson Comorbidity Index (`cci_total`)
2.  Severity stage at admission (`admission_stage`)

**Predictors include:** age (`age`), sex (`sex`), smoking status (`smoking`), marital status (`marital_status`), language (`language`), insurance type (`insurance_type`), race (`pat_race`), ethnicity (`ethnicity`), and area deprivation index (`ADI`).

# Load required packages

```{r Load required packages, include=F}
library(tidyverse)
library(tidymodels)
library(performance) # to calculate model performance and check model assumptions
library(sjPlot) # to create tables to compare regression output 
```

# Import and preview data

```{r Import and preview df}
df <- readRDS("/Users/sreynolds2/Documents/GitHub/MS-ADI/data/dm_stg_adi_7.19.21.rds")

head(df, n=10)
```

# Charlson Comorbidity Index (`cci_total`) as a function of ADI and demographics (non-hospital factors)

```{r Full model of CCI}
# Full model of CCI
m_CCI_full <- lm(cci_total ~ age + sex + smoking + marital_status + language + insurance_type + pat_race + ethnicity + ADI + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_CCI_full), confint.default(m_CCI_full, level=0.95)))

# Summarize regression output 
summary(m_CCI_full)

# Check model assumptions
check_model(m_CCI_full)

# Check model performance 
model_performance(m_CCI_full)
```

# Severity at admission (`admission_stage`) as a function of ADI, CCI, and demographics

```{r Full model of admission stage}
# Full model of admission stage
m_adm_stg_full <- lm(admission_stage ~ age + sex + smoking + marital_status + language + insurance_type + pat_race + ethnicity + ADI + cci_total + BMI, data = df)

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_adm_stg_full), confint.default(m_adm_stg_full, level=0.95)))

# Summarize regression output 
summary(m_adm_stg_full)

# Check model assumptions
check_model(m_adm_stg_full)

# Check model performance 
model_performance(m_adm_stg_full)
```

# Create table to compare regression model output

```{r Create table to compare model output}
tab_model(m_CCI_full, m_adm_stg_full,
          p.style = "numeric_stars",
          #show.reflvl = T,
          pred.labels = c("Intercept", "Age", "Male", "Non-Smoker", "Unknown Smoker", "Marital Status: Paired", "Marital Status: Unknown/Declined", "Not English", "Private Insurance", "Asian", "Black", "White", "Unknown/Declined Race", "Hispanic/Latino", "Not Hispanic", "Area Deprivation Index (ADI)", "Charlson Comorbidity Index (CCI)", "BMI"),
          dv.labels = c("CCI ~ Demog", "Severity at Admission ~ Demog + ADI + CCI"),
          title = 'Regression Models relating Demographics, CCI, ADI, and Severity at Admission')
```
