---
title: "Table One for Demog-Staging-ADI Data"
author: "Steph Reynolds (Stephanie.Reynolds@ucsf.edu)"
date: "`r format(Sys.time(), '%b %d, %Y  %H:%M %p')`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Background

## Project

MINDSCAPE: Modeling of infectious network dynamics for surveillance, control and prevention enhancement

## Description

This scripts reads in the demographics, Covid staging, and ADI data (`dm_stg_adi_7.19.21.rds`) and creates a Table 1 using both, `table1` and `tableone` packages.

## References (CRAN

-   `tableone`: Create 'Table 1' to Describe Baseline Characteristics with or
    without Propensity Score Weights ([Link](https://cran.r-project.org/web/packages/tableone/index.html))

-   `table1`: Tables of Descriptive Statistics in HTML ([Link](https://cran.r-project.org/web/packages/table1/))

# Install and load required packages

```{r Load required packages, include=F}
#install.packages("table1")
library(table1)
library(tableone)
library(tidyverse)
```

# Import and preview data

```{r Read in df}
# Read in data and assign to `df`
df <- readRDS("/Users/sreynolds2/Documents/GitHub/MS-ADI/data/dm_stg_adi_7.19.21.rds")

# Preview first n=10 lines 
head(df, n=10)

# View column names
colnames(df)

glimpse(df)
```

# Convert variables to factor type

```{r Convert to proper variable types }
# Identify all vars to be converted to factor type and assign to vector `fctvars`
fctvars <- c("cci_total", "ADI", "max_stage", "readmit", "end_in_death", "admission_stage", "severe_stg")

# Use lapply function to convert vars to factor
df[ ,fctvars] <- lapply(df[ , fctvars], factor)

# Check structure and var types
str(df)
```

# Assign variable labels and units

```{r Assign var labels and units}
label(df$age) <- "Age"
label(df$sex)       <- "Sex"
label(df$smoking)   <- "Smoking Status"
label(df$BMI)       <- "BMI"
label(df$cci_total) <- "CCI"
label(df$marital_status) <- "Marital Status"
label(df$language) <- "Language"
label(df$insurance_type) <- "Insurance Type"
label(df$pat_race) <- "Race"
label(df$ethnicity) <- "Ethnicity"
label(df$ADI) <- "Area Deprivation Index (ADI)"
label(df$max_stage)  <- "Max Severity"
label(df$readmit) <- "Readmit (Yes/No)"
label(df$hospital_LOS) <- "Hospital Length of Stay"
label(df$end_in_death) <- "Died in Hospital (Yes/No)"
label(df$admission_stage)  <- "Admission Severity"
label(df$severe_stg)  <- "Severe Morbidity and Mortality (Yes/No)"

units(df$age)       <- "years"
units(df$hospital_LOS) <- "days"
```

# Create Table 1 using `table1` package

```{r table1 package}
# Run table1 function with all variables 
t1 <- table1::table1(~ age + sex + smoking + BMI + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + ADI + max_stage + readmit + hospital_LOS + end_in_death + admission_stage + severe_stg,
       data = df)

# table1::knit_print.table1(t1)
# Error: 'knit_print.table1' is not an exported object from 'namespace:table1'

# table1::as.data.frame.table1(t1)
# Error: 'as.data.frame.table1' is not an exported object from 'namespace:table1'
```

# Create Table 1 using `tableone` package

```{r tableone package}
# Assign col names to `vars` vector
vars <- colnames(df)[-1]

# Assign var labels to `labs` vector
labs <- c("Age", "Sex", "Smoking Status", "BMI", "CCI", "Marital Status", "Language", "Insurance Type", "Race", "Ethnicity", "Area Deprivation Index (ADI)", "Max Severity", "Readmit (Yes/No)",  "Hospital Length of Stay", "Died in Hospital (Yes/No)", "Admission Severity", "Severe Morbidity and Mortality (Yes/No)")

# Create Table One
tableOne <- CreateTableOne(data = df, vars, includeNA = T)

# Summary of continuous and categorical vars
summary(tableOne)

# Print table one
print(tableOne,
      showAllLevels = T, 
      nonnormal = "hospital_LOS")

# If you want to copy to Excel or Word, then set quote = TRUE
print(tableOne, nonnormal = "hospital_LOS", quote = TRUE)

# If you want to center-align values in Word, then set noSpaces = TRUE
print(tableOne, nonnormal = "hospital_LOS", quote = TRUE, noSpaces = TRUE)
```
