---
title: "Regression Analysis for Demog-Staging-ADI Data -- Primary Outcome: Severe Morbidity and Mortality (SMM)"
author: "Steph Reynolds (Stephanie.Reynolds@ucsf.edu)"
date: "`r format(Sys.time(), '%b %d, %Y  %H:%M %p')`"
output:
  html_document:
    toc: true
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

# Background

## Project 
MINDSCAPE: Modeling of infectious network dynamics for surveillance, control and prevention enhancement

## Description
This file reads in the demographics, Covid staging, and ADI data (`dm_stg_adi_7.19.21.rds`) and fits a logistic regression model with severe morbidity and mortality (`severe_stg`) as the outcome. Primary and secondary outcomes for full regression analysis can be found below. 

## Primary Outcome 

  * Morbidity and Mortality (`severe_stg`) -> All patients who reached a max stage of 6+ (severe) were recoded as severe_stg = 1

## Secondary Outcomes

  * Length of Stay (`LOS`) -> Length of stay that patients were hospitalized
    * Only patients who were hospitalized for >= 1 day - aka inpatients - were included in the regression analysis.
  * Readmit (`readmit`) --> Patients who were readmitted to hospital within 30(?) days

# Load required packages
```{r Load required packages, include=F}
library(tidyverse)
library(tidymodels)
library(performance) # to calculate model performance and check model assumptions
```

# Import and preview data
```{r Read in df}
df <- readRDS("/Users/sreynolds2/Documents/GitHub/MS-ADI/data/dm_stg_adi_7.19.21.rds")

head(df, n=10)
```

# Compare full and null models -- Severe morbidity and mortality (`severe_stg`)
```{r Full and null models of LOS}
# FULL MODEL 
m_full <- glm(severe_stg ~ age + sex + smoking + cci_total + marital_status + language + insurance_type + pat_race + ethnicity + ADI, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_full), confint.default(m_full, level=0.95)))

# Summarize regression output 
summary(m_full)

# Check model assumptions
check_model(m_full)

# Check model performance 
model_performance(m_full)

# NULL MODEL 
m_null <- glm(severe_stg ~ 1, data = df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_null), confint.default(m_null, level=0.95)))

# Summarize regression output 
summary(m_null)

# Check model performance 
model_performance(m_null)

```

# Generate simple logistic regressions for severe morbidity and mortality

## Severe_stg ~ age
```{r Severe_stg ~ age}
m_sev_age <- glm(severe_stg ~ age, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_age), confint.default(m_sev_age, level=0.95)))

# Summarize regression output 
summary(m_sev_age)

# Check model assumptions
check_model(m_sev_age)

# Check model performance 
model_performance(m_sev_age)
```

## Severe_stg ~ sex 
```{r Severe_stg ~ sex}
m_sev_sex <- glm(severe_stg ~ sex, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_sex), confint.default(m_sev_sex, level=0.95)))

# Summarize regression output 
summary(m_sev_sex)

# Check model assumptions
check_model(m_sev_sex)

# Check model performance 
model_performance(m_sev_sex)
```

## Severe_stg ~ smoking
```{r Severe_stg ~ smoking}
m_sev_smoke <- glm(severe_stg ~ smoking, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_smoke), confint.default(m_sev_smoke, level=0.95)))

# Summarize regression output 
summary(m_sev_smoke)

# Check model assumptions
check_model(m_sev_smoke)

# Check model performance 
model_performance(m_sev_smoke)
```

## Severe_stg ~ Charlston Comorbidity Index (CCI)
```{r Severe_stg ~ cci}
m_sev_cci <- glm(severe_stg ~ cci_total, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_cci), confint.default(m_sev_cci, level=0.95)))

# Summarize regression output 
summary(m_sev_cci)

# Check model assumptions
check_model(m_sev_cci)

# Check model performance 
model_performance(m_sev_cci)
```

## Severe_stg ~ marital status
```{r Severe_stg ~ marital_status}
m_sev_marital <- glm(severe_stg ~ marital_status, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_marital), confint.default(m_sev_marital, level=0.95)))

# Summarize regression output 
summary(m_sev_marital)

# Check model assumptions
check_model(m_sev_marital)

# Check model performance 
model_performance(m_sev_marital)
```

## Severe_stg ~ language
```{r Severe_stg ~ language}
m_sev_language <- glm(severe_stg ~ language, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_language), confint.default(m_sev_language, level=0.95)))

# Summarize regression output 
summary(m_sev_language)

# Check model assumptions
check_model(m_sev_language)

# Check model performance 
model_performance(m_sev_language)
```

## Severe_stg ~ insurance type
```{r Severe_stg ~ insurance_type}
m_sev_insur <- glm(severe_stg ~ insurance_type, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_insur), confint.default(m_sev_insur, level=0.95)))

# Summarize regression output 
summary(m_sev_insur)

# Check model assumptions
check_model(m_sev_insur)

# Check model performance 
model_performance(m_sev_insur)
```

## Severe_stg ~ race
```{r Severe_stg ~ race}
m_sev_race <- glm(severe_stg ~ pat_race, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_race), confint.default(m_sev_race, level=0.95)))

# Summarize regression output 
summary(m_sev_race)

# Check model assumptions
check_model(m_sev_race)

# Check model performance 
model_performance(m_sev_race)
```

## Severe_stg ~ ethnicity
```{r Severe_stg ~ ethnicity}
m_sev_ethnicity <- glm(severe_stg ~ ethnicity, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_ethnicity), confint.default(m_sev_ethnicity, level=0.95)))

# Summarize regression output 
summary(m_sev_ethnicity)

# Check model assumptions
check_model(m_sev_ethnicity)

# Check model performance 
model_performance(m_sev_ethnicity)
```

## Severe_stg ~ Area Deprivation Index (ADI)
```{r Severe_stg ~ adi}
m_sev_adi <- glm(severe_stg ~ ADI, df, family = 'binomial')

# Odds ratio of coefficients
exp(cbind("Odds ratio"=coef(m_sev_adi), confint.default(m_sev_adi, level=0.95)))

# Summarize regression output 
summary(m_sev_adi)

# Check model assumptions
check_model(m_sev_adi)

# Check model performance 
model_performance(m_sev_adi)
```

# End of document 
